---
title: "eMOLT Status Report"
date: "`r Sys.Date()`"
output: html_document
params:
  tech: "RUTGERS"
  timeframe: "month"
  filepath: "C:/Users/george.maynard/Documents/emolt_project_management"
---

```{r python_queries, echo=FALSE,warning=FALSE,message=FALSE,error=FALSE,include=FALSE}
vessel_filename=paste0(
  params$filepath,
  "/VesselCheckIns/",
  params$tech,
  "/vessels.csv"
)
reticulate::source_python(paste0(params$filepath,"/VesselCheckIns/utility_functions/list_portal_boats.py"))
portal_vessels=reticulate::py_run_string('list_portal_boats()')
portal_vessels=portal_vessels$boat_names
reticulate::source_python(paste0(params$filepath,"/VesselCheckIns/utility_functions/list_s3_and_db.py"))
s3_only=list_s3_and_db(vessel_filename)[1][[1]]
db_only=list_s3_and_db(vessel_filename)[2][[1]]
```

```{r vessels, echo=FALSE}
vessels=read.csv(vessel_filename)
```

```{r reports, echo=FALSE,include=FALSE}
report_filename=paste0(
  params$filepath,
  "/VesselCheckIns/last_",
  params$timeframe,
  "_ddh_reports.csv"
)
reports=read.csv(report_filename)
reports$VESSEL_NAME = gsub("_"," ",reports$VESSEL_NAME)
reports=subset(reports,reports$VESSEL_NAME%in%vessels$VESSEL_NAME)
latest_DDH=max(reports$DDH_SW_VERSION)
latest_bluez=max(reports$DDH_BLUEZ_VERSION)
inventory=read.csv(paste0(params$filepath,"/VesselCheckIns/equipment_inventory.csv"))
intervals=read.csv(paste0(params$filepath,"/VesselCheckIns/equipment_maintenance_intervals.csv"))
inventory$CALIBRATION_DATE=lubridate::ymd(inventory$CALIBRATION_DATE)
inventory$BATTERY_CHANGE=lubridate::ymd(inventory$BATTERY_CHANGE)
inventory$CALIBRATION_DUE=NA
inventory$BATTERY_DUE=NA
intervals$LOGGER=paste(intervals$EQUIPMENT_MAKE,intervals$EQUIPMENT_MODEL)
## Calculate maintenance due dates
for(i in 1:nrow(inventory)){
 logger=paste(inventory$MAKE[i],inventory$MODEL[i])
 logger_int=subset(intervals,intervals$LOGGER==logger)
 if(nrow(logger_int)>0){
   inventory$BATTERY_DUE[i]=ifelse(
   is.na(inventory$BATTERY_CHANGE[i])==FALSE,
   inventory$BATTERY_CHANGE[i]+lubridate::dmonths(logger_int[which(logger_int$EQUIPMENT_MAINTENANCE_EVENT=="Battery Replaced"),"EQUIPMENT_MAINTENANCE_INTERVAL_MONTHS"]),
   NA
 )
 inventory$CALIBRATION_DUE[i]=ifelse(
   is.na(inventory$CALIBRATION_DATE[i])==FALSE,
   inventory$CALIBRATION_DATE[i]+lubridate::dmonths(logger_int[which(logger_int$EQUIPMENT_MAINTENANCE_EVENT%in%c("Calibration Check","Factory Calibration")),"EQUIPMENT_MAINTENANCE_INTERVAL_MONTHS"]),
   NA
 )
 }
}
```

This report covers time between `r min(lubridate::ymd_hms(reports$TIME_LOCAL_STR))` and `r max(lubridate::ymd_hms(reports$TIME_LOCAL_STR))` for vessels supported by `r params$tech` and includes the following vessels: 

```{r vessel_names, include=TRUE, echo=FALSE}
print(vessels$VESSEL_NAME)
action_items=data.frame(
  action=as.character(),
  vessel=as.character(),
  state=as.character(),
  port=as.character(),
  assignee=as.character(),
  logger=as.character(),
  notes=as.character()
)
```

## Inactive Vessels

Of the `r nrow(vessels)` vessels included in the report, `r sum(vessels$VESSEL_NAME%in%reports$VESSEL_NAME==FALSE)` were inactive during the reporting period (`r round(sum(vessels$VESSEL_NAME%in%reports$VESSEL_NAME==FALSE)/nrow(vessels)*100,0)`%). Those inactive vessels include the following:

```{r inactive_vessels, include=TRUE, echo=FALSE, results='asis'}
inactive=subset(vessels,vessels$VESSEL_NAME%in%reports$VESSEL_NAME==FALSE)
if(nrow(inactive)>0){
    cat(paste0("- [ ]  ",inactive$VESSEL_NAME), sep="\n")
  newai = data.frame(
    action="Contact vessel to determine whether system is powered off or vessel is not fishing",
    vessel=inactive$VESSEL_NAME,
    state=inactive$STATE_POSTAL,
    port=inactive$PORT_NAME,
    assignee=params$tech,
    logger=NA,
    notes=paste0(inactive$FIRST_NAME," ",inactive$LAST_NAME," Phone: ",inactive$PHONE," email: ",inactive$EMAIL)
  )
  if(nrow(newai)>0){
    action_items=rbind(action_items,newai)
    rm(newai)
  }
} else {
  cat("\nNo inactive vessels found\n")
}

```

## Active Vessels

```{r vessel_status_reports, include=TRUE, echo=FALSE, results='asis'}
active=subset(vessels,vessels$VESSEL_NAME%in%reports$VESSEL_NAME==TRUE)
for(v in active$VESSEL_NAME){
  v_reports=subset(reports,reports$VESSEL_NAME==v)
    info_list=list(
    name = v,
    downloads = subset(v_reports,v_reports$REASON_NAME=="DDH_NOTIFICATION_OK_LOGGER_DL"),
    DDH_SW = list(unique(v_reports$DDH_SW_VERSION)),
    BLE_antenna = list(unique(v_reports$DDH_BLE_ANTENNA)),
    bluez = list(unique(v_reports$DDH_BLUEZ_VERSION))
  )
  v_info=subset(active,active$VESSEL_NAME==v)
  cat("\n### ",v,"\n")
  if(max(v_reports$DDH_SW_VERSION)==latest_DDH){
    cat("\n- This DDH is running the latest software version.\n")
  } else {
    cat("\n- The software on this DDH is an older version and should be updated.\n")
    newai=data.frame(
      action="Update DDH Software",
      vessel=v,
      state=subset(active,active$VESSEL_NAME==v)$STATE_POSTAL,
      port=subset(active,active$VESSEL_NAME==v)$PORT_NAME,
      assignee="Huanxin",
      logger=NA,
      notes=paste0("currently running: ",max(v_reports$DDH_SW_VERSION)," newest: ", latest_DDH)
    )
    action_items=rbind(action_items,newai)
    rm(newai)
  }
  cat("\n- This deckbox has an ",info_list$BLE_antenna[[1]]," bluetooth antenna.\n")
  if(max(v_reports$DDH_BLUEZ_VERSION)==latest_bluez){
    cat("\n- This DDH is running the latest bluetooth driver.\n")
  } else {
    cat("\n- The software on this DDH has an older bluetooth driver and should be updated.\n")
  }
  errors=subset(v_reports,v_reports$REASON_NAME%in%c(
    'DDH_NOTIFICATION_ERROR_HW_BLE',
    'DDH_NOTIFICATION_ERROR_HW_LOGGER_OXYGEN',
    'DDH_NOTIFICATION_ERROR_HW_LOGGER_BATTERY',
    'DDH_NOTIFICATION_ERROR_HW_LOGGER_PRESSURE',
    'DDH_NOTIFICATION_ERROR_HW_LOGGER_RETRIES',
    'DDH_NOTIFICATION_ERROR_SW_AWS_S3',
    'DDH_NOTIFICATION_ERROR_SW_CRASH'
  ))
  if(nrow(errors)>0){
    errors=errors[,c('TIME_LOCAL_STR','REASON_NAME','LOGGER_SN','LOGGER_GFV')]
    errors$LOGGER_SN=ifelse(errors$LOGGER_SN=="",NA,errors$LOGGER_SN)
    cat("\n#### Errors Reported\n")
    error_table=knitr::kable(errors,format="markdown")
    cat(error_table,sep="\n")
    newai=data.frame(
      action="Evaluate error reports",
      vessel=v,
      state=subset(active,active$VESSEL_NAME==v)$STATE_POSTAL,
      port=subset(active,active$VESSEL_NAME==v)$PORT_NAME,
      assignee=params$tech,
      logger=ifelse(is.na(errors$LOGGER_SN),NA,cli::ansi_collapse(unique(errors$LOGGER_SN))),
      notes="Errors reported, please verify functionality and troubleshoot with George and Huanxin as necessary"
      )
    newai=unique(newai)
    action_items=rbind(action_items,newai)
    rm(newai)
  }
  cat("\n#### Loggers\n")
  if(length(unique(info_list$downloads$LOGGER_SN))==0){
    cat("\nNO LOGGERS DEPLOYED\n")
    newai=data.frame(
        action="Check DDH for logger assignments and check vessel to ensure logger is present",
        vessel=v,
        state=subset(active,active$VESSEL_NAME==v)$STATE_POSTAL,
        port=subset(active,active$VESSEL_NAME==v)$PORT_NAME,
        assignee=params$tech,
        logger=NA,
        notes=paste0(v_info$FIRST_NAME," ",v_info$LAST_NAME," Phone: ",v_info$PHONE," email: ",v_info$EMAIL)
      )
    action_items=rbind(action_items,newai)
    rm(newai)
  }
  for (l in unique(info_list$downloads$LOGGER_SN)){
    x=subset(info_list$downloads, info_list$downloads$LOGGER_SN==l)
    if(grepl("[-_]",l)){
      sn=as.numeric(strsplit(l,"[-_]")[[1]][2])
      y=subset(inventory,inventory$SERIAL_NUMBER==sn)
    } else {
      y=subset(inventory,inventory$SERIAL_NUMBER==as.numeric(l))
    }
    maintenance=list(
      last_cal=max(y$CALIBRATION_DATE),
      last_bat=max(y$BATTERY_CHANGE),
      rec_cal=max(y$CALIBRATION_DUE),
      rec_bat=max(y$BATTERY_DUE)
    )
    cat("\n Logger: ",l,y$MAKE,y$MODEL,"\n")
    cat("\n- Last Download: ", max(x$TIME_LOCAL_STR),"\n")
    cat("\n- Last Recalibration: ",strftime(maintenance$last_cal,format="%Y-%m-%d"),"\n")
    cat("\n- Calibration Check Due: ",strftime(maintenance$rec_cal,format="%Y-%m-%d"),"\n")
    cat("\n- Last Battery Change: ",strftime(maintenance$last_bat),"\n")
    cat("\n- Battery Change Due: ",strftime(maintenance$rec_bat,format="%Y-%m-%d"),"\n")
    if(is.na(maintenance$rec_bat)){
      newai=data.frame(
        action="Add battery maintenance record to database",
        vessel=NA,
        state=NA,
        port=NA,
        assignee="George",
        logger=l,
        notes="Use last calcheck or first deployment if known"
      )
      action_items=rbind(action_items,newai)
      rm(newai)
    } else {
      if(as.POSIXct(maintenance$rec_bat)<Sys.Date()){
        newai=data.frame(
          action="Replace batteries",
          vessel=v,
          state=subset(active,active$VESSEL_NAME==v)$STATE_POSTAL,
          port=subset(active,active$VESSEL_NAME==v)$PORT_NAME,
          assignee=params$tech,
          logger=l,
          notes=paste0(v_info$FIRST_NAME," ",v_info$LAST_NAME," Phone: ",v_info$PHONE," email: ",v_info$EMAIL)
        )
        action_items=rbind(action_items,newai)
        rm(newai)
      }
    }
    if(is.na(maintenance$rec_cal)){
      newai=data.frame(
        action="Add logger calibration record to database",
        vessel=v,
        state=NA,
        port=NA,
        assignee="George",
        logger=l,
        notes="Use first deployment if known"
      )
      action_items=rbind(action_items,newai)
      rm(newai)
    } else {
      if(as.POSIXct(maintenance$rec_cal)<Sys.Date()){
        newai=data.frame(
          action="Check logger calibration",
          vessel=v,
          state=subset(active,active$VESSEL_NAME==v)$STATE_POSTAL,
          port=subset(active,active$VESSEL_NAME==v)$PORT_NAME,
          assignee=params$tech,
          logger=l,
          notes=paste0(v_info$FIRST_NAME," ",v_info$LAST_NAME," Phone: ",v_info$PHONE," email: ",v_info$EMAIL)
        )
        action_items=rbind(action_items,newai)
        rm(newai)
      }
    }
  }
  
}
```

## Action Items
```{r action_items, echo=FALSE,results='asis'}
hx=subset(action_items,action_items$assignee=="Huanxin")
gm=subset(action_items,action_items$assignee=="George")
tech=subset(action_items,action_items$assignee==params$tech)

cat("\n### Tech to do\n\n")
tech_to_do=knitr::kable(tech)
cat(tech_to_do,sep="\n")

cat("\n### Huanxin to do\n\n")
hx_to_do=knitr::kable(hx)
cat(hx_to_do,sep="\n")

cat("\n### George to do\n\n")
gm_to_do=knitr::kable(gm)
cat(gm_to_do,sep="\n")
```
