---
title: "eMOLT Weekly Update"
author: "George Maynard"
date: "`r Sys.Date()`"  
output: 
  blastula::blastula_email:
    toc: FALSE
    toc_depth: 3
    toc_float: TRUE
    fig_caption: FALSE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(blastula)
library(marmap)
library(rstudioapi)
source("C:/Users/george.maynard/Documents/GitHubRepos/emolt_serverside/API/API_header.R")
today=Sys.Date()
lastWeek=today-days(7)
db_config=config::get(file="C:/Users/george.maynard/Documents/GitHubRepos/emolt_serverside/API/config.yml")$dev_intranet
conn=dbConnector(db_config)
```

<center> 

<font size="5"> *eMOLT Weekly Update `r Sys.Date()` * </font>

</center>

### Weekly Recap 

The 2023 drifter season got underway with a [link to plot]('https://studentdrifters.org/tracks/drift_fpds_2023_1.html') deployment in the Gulf of Mexico.  Erin Pelletier is working with the lead teacher to tell a very interesting story coming out soon concerning this one drifter. For now, you can download and view a [link to video]('https://studentdrifters.org/tracks/drift_fpds_2023_1.mp4v') 3-minute deployment video relating part of the story. A few dozen more drifter deployments are planned this Spring on the Northeast Shelf.  One was deployed by the USCG on 11 March in Cape Cod Bay [link to plot]('https://studentdrifters.org/tracks/drift_fhs_2023_1.html'), stranded on the Plymouth beaches four days later during the early stages of the Northeaster and recovered by a helpful beachwalker.

In less exciting news, the 2023 red tide sampling season is underway in Massachusetts, and DMF has implemented a shellfish harvest closure in parts of the Nauset estuary in Orleans and Eastham. For further information about specific areas impacted by the closure, please see the [full notice](https://www.mass.gov/doc/3823-psp-red-tide-closure-notice-for-the-harvest-of-all-shellfish-in-nauset-system/download). Red tides are [harmful algal blooms](https://oceanservice.noaa.gov/facts/redtide.html) the occur under specific environmental conditions, such as warm surface water, low salinity, and high nutrient availability. Even after the blooms recede, they may still cause additional problems for shellfish fisheries through the development of low-oxygen zones as the dead algae decompose.  
### Realtime Summary (Vessels with Rockblock Satellite Transmitters)

This week, we received `r nrow(dbGetQuery(conn=conn,statement=paste0("SELECT * FROM VESSEL_STATUS WHERE TIMESTAMP >'", lastWeek, "' AND REPORT_TYPE = 'SUMMARY_DATA' AND VESSEL_ID != 23")))` haul-averaged reports from `r nrow(dbGetQuery(conn=conn, statement=paste0("SELECT DISTINCT VESSEL_ID FROM VESSEL_STATUS WHERE TIMESTAMP >'", lastWeek,"' AND REPORT_TYPE = 'SUMMARY_DATA' AND VESSEL_ID != 23")))` vessels. 

```{r statusPlot, dev='png',echo=FALSE, fig.width=8,fig.height=6,fig.show='hide',include=FALSE}
dbDisconnectAll()
conn=dbConnector(db_config)
lastweek=Sys.Date()-days(7)
data=dbGetQuery(
  conn=conn,
  statement=paste0(
    "SELECT * FROM VESSEL_STATUS WHERE TIMESTAMP > '",
    lastweek,
    "' AND VESSEL_ID != 23"
  )
)
data=select(data,REPORT_TYPE,LATITUDE,LONGITUDE,TIMESTAMP)
bath=readGEBCO.bathy(
  file="C:/Users/george.maynard/Documents/GitHubRepos/emolt_project_management/UtilityScripts/GEBCO/gebco_2022_n47.0_s38.0_w-76.0_e-59.0.nc",
  resolution=10
)
## Create color ramp
blues=c(
  "lightsteelblue4", 
  "lightsteelblue3",
  "lightsteelblue2", 
  "lightsteelblue1"
)
## Plotting the bathymetry with different colors for land and sea
plot(
  bath,
  step=100,
  deepest.isobath=-1000,
  shallowest.isobath=0,
  col="darkgray",
  image = TRUE, 
  land = TRUE, 
  lwd = 0.1,
  bpal = list(
    c(0, max(bath), "gray"),
    c(min(bath),0,blues)
  ),
  main=paste0("ALL eMOLT VESSELS with Satellite Transmitters \nREPORTS FROM: ",lastweek," to ",Sys.Date())
)
## Plot the status report locations
x=subset(data,data$REPORT_TYPE=="SHORT_STATUS")
points(
  x$LATITUDE~x$LONGITUDE,
  pch=1,
  col='red',
  cex=2
)
## Plot data uploads
x=subset(data,data$REPORT_TYPE=="SUMMARY_DATA")
points(
  x$LATITUDE~x$LONGITUDE,
  pch=1,
  col='blue',
  cex=2
)
legend(
  'topleft',
  col=c('blue','red'),
  legend=c('Summary Data Upload','Status Report'),
  pch=c(1,1),
  bty='n',
  bg=NULL,
  border='black'
)
```

![Status plot.](`r knitr::fig_chunk('statusPlot', 'png')`)
*Figure 3 - eMOLT Satellite Transmitter status plot for the previous week.*
In the figure above, you can see the approximate locations where we received "Status Reports" (a ping from your system letting us know that it's still working) and "Data Uploads" (actual temperature / depth data collected by your probes). The "Status Reports" come in every 12 hours or so when a system is powered up. "Data Uploads" only come in when you haul the probes. If you were out fishing and don't see your approximate locations on here, please reach out because there may be a problem with your system.

### Announcements
Glad to hear many of you were at the Maine Fishermen's Forum. Sorry we missed it.

For those of you who missed the workshop at WHOI back in January, you can view the full recordings/videos at https://www.us-ocb.org/coastal-bgc-obs-network-with-fishing-community/. Just click on the blue "Watch Recordings" button.

All the best,
George and JiM
